outlier_exploration

### 2025-05-07 Kyubin's Edit/KYUBIN_EDIT.qmd
line 275 Added a message that explains where the editing was left off at

# get rid of 3 highest aux r^2 adj and high VIF scores: Age and Quality of sleep
model_vif <- lm(sleep_duration ~gender + bmi_category + stress_level +  
                    physical_activity_level + occupation + 
                    heart_rate + daily_steps + 
                    sleep_disorder + PP, data = sleep_test)

@@

# 3. Forward Selection
# Define the full scope and a null model
full_scope <- formula(model_vif)
null_model <- lm(sleep_duration ~ 1, data = sleep)

@@

>>>>

# get rid of 2 highest aux r^2 adj and high VIF scores: Age and Quality of Sleep
model_vif <- lm(sleep_duration ~gender + bmi_category  +
                    physical_activity_level + occupation + 
                    heart_rate + daily_steps + 
                    sleep_disorder + PP + stress_level, data = sleep_test)

@@

# 3. Forward Selection
# Define the full scope and a null model
full_scope <- formula(model_vif)
null_model <- lm(sleep_duration ~ 1, data = sleep_test)

@@

#### ALL THE CODE BELOW THIS HAS NOT BEEN EDITED! STILL NEED TO CHANGE "sleep" TO "sleep_test" AND CHANGE "bmi_category" TO "age" ####
